---
title: "Linguistic Analysis of Speech Given at Congressional Testimony and Hearings"
author: "Edward Zhao"
date: "2021-05-01"
bibliography: reference.bib
output: 
  html_notebook:
    toc: yes
    code_folding: hide
    css: style.css
---

# 1.0 Preface #
## 1.1 Background ##
Linguistic analysis is the scientific analysis of language to capture its characteristics. In particular, the analysis of syntax, semantics, and pragmatics allows for the interpretation of language features at the content level, including sentence structure, meaning, and social use [@lapham_2021]. By practicing linguistic analysis, we gain a deeper understanding of a language, which helps us improve the competence of using language.

## 1.2 Purpose ##
In the congressional testimony and hearings scenario, we perform a linguistic analysis of the speakers' speech to gain information. This analysis will reveal the general characteristics of people's speech in a given scenario. Further, the analysis will compare the speech characteristics of people with different identities. By summarizing the speech characteristics, this analysis will help people who wish to participate in congressional testimony and hearings to improve their articulation and professionalism.

## 1.3 Data Usage ##
Data used in this analysis is based on audio and video transcripts of congressional testimonies and congressional hearings. This includes US Senate testimonies, US House of Representatives hearings, and international hearings that are publicly televised [@rev_2021]. The dataset is generated by a <a href="https://github.com/ED9426/Linguistic-Analysis/blob/main/DataRetrieve.py">Python script</a> with transcripts from <a href="https://www.rev.com/blog/transcript-category/congressional-testimony-hearing-transcripts">Rev</a>.

## 1.4 Assumptions ##
The analysis of this report is based on the following assumptions:

- Only the period (.), question mark (?), and exclamation mark (!) mark the end of a sentence. "And I’ve tried… These are important enough questions." is counted as one sentence.
- A concession sentence refers to a sentence containing "though" or "although."
- Declarative sentences are sentences ending with a period. The declarative sentence consists of only affirmative sentences and negative sentences. Negative sentences are sentences that contain "not" or "n't", so “negative” here is not related to sentiment.
- Questions are sentences that contain question marks.
- Exclamatory sentences are sentences that contain exclamation marks.
- "Scholar" refers to people whose title includes "Dr" or "Prof".
- "President" refers to a person who has run for president, whether won or not.
- "Entrepreneur" in this report includes (Bill) Gates, (Mark) Zuckerberg, (Tim) Cook.

<!-- load libraries and clean the environment, import data-->
```{r setUp, include=FALSE}
knitr::opts_chunk$set(fig.dim=c(8,3),
                      fig.align = "center",
                      warning = FALSE)
library(tidyverse)
library(tidytext)
library(kableExtra)
library(grid)
library(gridExtra)
rm(list=ls())

df <- read_csv("Congressional Testimony & Hearing Transcripts.csv") %>% # load data
  mutate(speech = str_replace_all(speech, "it’s|It’s|we’re|We’re|i’m|I’m|that’s|That’s|we’ve|We’ve|you’re|You’re", ""), 
         speech = str_replace_all(speech, "i’ve|I’ve|there’s|There’s|they’re|They’re|you’ve|You’ve|i’ll|I’ll", ""),
         speech = str_replace_all(speech, "Mr\\.|Ms\\.|Mrs\\.|Jr\\.|Sec\\.|Hon\\.|Cap\\.|\\.\\.|S\\.|C\\.|A\\.|H\\.|R\\.", ""),
         speech = str_replace(speech, "Dr.", "Dr"),
         speech = str_replace(speech, "Prof.", "Prof"),
         speech = str_replace(speech, "Sen.", "Sen"),
         speech = str_replace(speech, "Rep.", "Rep"),
         speech = str_replace(speech, "V\\.P\\.", "VP")) %>% 
  na.omit()
data("stop_words") # import stop words
```

# 2.0 General Analysis #
## 2.1 Word Analysis ##
```{r wordOccurenceAnalysis}
# processes data into individual words without stop words
word <- df %>% 
  unnest_tokens(word, speech) %>% 
  anti_join(stop_words, by = "word")
# word useage statistics
word %>% 
  count(word, sort = TRUE) %>% 
  rename("Number of Occurrences" = n) %>% 
  kable(caption="Number of Words") %>% 
  kable_styling(full_width = FALSE, position = "l") %>% 
  scroll_box(height="400px")
# visualization
word %>% 
  count(word, sort = TRUE) %>%
  head(50) %>% 
  mutate(Word = reorder(word, n)) %>%
  ggplot(aes(Word, n)) +
  geom_col(position = "dodge") +
  ggtitle("The 50 Most Frequent Words") +
  labs(y = "Number of Occurrences") +
  guides(x =  guide_axis(angle = 45))
```

Based on the plot, we can see that the speeches in the congressional testimony and hearings are dominated by politics and current events. Politics includes domestic politics and international relations. Current events are mainly the presidential election and the epidemic.

```{r wordLengthStatistics}
n = str_count(word$word, ".") # word length
# summarize word length
summary(n)
tibble(n) %>% 
  filter(n < 13) %>% # remove outliers
  ggplot(aes(y = n)) + 
  geom_boxplot(notch = TRUE) + 
  ggtitle("Word Length Distribution") +
  ylab("Word Length")
```

The table and plot indicate that words range in length from 1 to 34 and that the middle 50% of words are in the 5-9 range. the median is 7 and the mean is 6.959. However, the average length of English words is only 4.79, and 80% of them are in the 2-7 range [@norvig_2013]. This indicates that the average length of words in congressional testimony and hearings is much greater than the average.

## 1.2 Sentence Analysis ##
```{r speechLengthStatistics, message=FALSE}
# count length of speech
len <- sapply(str_split(df$speech, " "), length)
sentence <- tibble(n = seq(1,length(len),1),
                   len,
                   avg = mean(len),
                   med = median(len),
                   speech = df$speech)
# summarize speech length
summary(len)
sentence %>% 
  filter(len < 180) %>% # remove outliers
  ggplot(aes(y = len)) + 
  geom_boxplot(notch = TRUE) + 
  ggtitle("Speech Length Distribution") + 
  ylab("Speech Length")
```

The table and plot point out that in congressional testimony and hearings, the length of each speech is distributed between 1 and 503, while the middle 50% is 9-85. The mean length 52.28 is greater than the median 33, which shows that the distribution of sentence length is right-skewed.

```{r speechLengthVisualization, message=FALSE}
ggplot(data = sentence) + 
  geom_smooth(aes(n, len, color = "speech length"), se = FALSE) + 
  geom_smooth(aes(n, len, color = "speech length regression"), se = FALSE, method = lm) + 
  geom_hline(aes(yintercept = avg, color = "average sentiment value"), linetype = "dashed") + 
  geom_hline(aes(yintercept = med, color = "median sentiment value"), linetype = "dotted") + 
  labs(x = "Order of Speech", 
       y = "Speech Length", 
       title = "Speech Length Visualization")
```

As with the box plot, this plot also exhibits that the mean length of speech is significantly higher than the median length. The Order of Speech is in chronological order from near to far, so the regression line shows that the most recent congressional testimony and hearings are longer than the previous ones. Alternatively, the length of speech is increasing over time.

```{r sentenceTypeAnalysis}
temp <- sentence %>% 
  summarize(declarative = sum(str_count(speech, "\\.")),
            question = sum(str_count(speech, "\\?")),
            exclamatory = sum(str_count(speech, "!")),
            negative = sum(str_count(speech, "not|Not|’t")),
            affirmative = declarative - negative,)
# overview
temp
```

```{r sentenceTypeComparison}
# sentence type ratio by tone
p1 <- temp %>% 
  pivot_longer(cols = c("declarative", "question", "exclamatory"), 
               names_to = "type", 
               values_to = "value") %>% 
  select(type, value) %>% 
  mutate(ratio = value / sum(value)) %>% 
  ggplot(aes(x = "", y = value, fill = type)) + 
  geom_bar(width = 1, stat = "identity") + 
  geom_text(aes(label = paste(as.character(round(ratio, 4)*100),"%", sep = "")), 
            color = "white", check_overlap = TRUE, vjust = -3) + 
  coord_polar("y") + 
  labs(x = NULL, y = NULL, title = "Sentence Type Ratio", subtitle = "based on tone", fill = "tone") + 
  theme(legend.position="bottom")

# sentence type ratio by attitude
p2 <- temp %>% 
  pivot_longer(cols = c("affirmative", "negative"), 
               names_to = "type",
               values_to = "value") %>% 
  select(type, value) %>% 
  mutate(ratio = value / sum(value)) %>% 
  ggplot(aes(x = "", y = value, fill = type)) + 
  geom_bar(width = 1, stat = "identity") + 
  geom_text(aes(label = paste(as.character(round(ratio, 4)*100),"%", sep = "")), 
            color = "white", check_overlap = TRUE, vjust = -3) + 
  coord_polar("y") + 
  labs(x = NULL, y = NULL, title = "Sentence Type Ratio", subtitle = "based on attitude", fill = "attitude") + 
  theme(legend.position="bottom")

grid.arrange(p1, p2, ncol = 2)
```

The exclamatory sentence is not a popular sentence type on congressional testimony and hearings, judging from the fact that it appears only 26 times in total, or 0.01%. Declarative sentences dominate the statements, followed by questions. In terms of attitude, affirmative sentences accounted for 77.15% while negative sentences accounted for 22.85%, which shows that affirmative sentences were the mainstay of the speech.

## 1.3 Sentiment Analysis ##
```{r sentimentRatio}
sentiment <- word %>% 
  inner_join(get_sentiments("bing"), by = "word") %>% 
  inner_join(get_sentiments("afinn"), by = "word")

# sentiment ratio
sentiment %>% 
  count(sentiment, sentiment) %>% 
  mutate(ratio = n / sum(n)) %>% 
  ggplot(aes(x = "", y = n, fill = sentiment)) + 
  geom_bar(width = 1, stat = "identity") + 
  geom_text(aes(label = paste(as.character(round(ratio, 4)*100),"%", sep = "")), 
            color = "white", vjust = -6) + 
  coord_polar("y") + 
  labs(x = NULL, y = NULL, title = "Sentiment Ratio")
```

In terms of sentiment, the statements in congressional testimony and hearings are predominantly negative.

```{r sentimentStatistics}
# sentiment value
summary(sentiment$value)
ggplot(sentiment, aes(y = value)) + 
  geom_boxplot(notch = TRUE) + 
  ggtitle("Sentiment Value Distribution")
```

```{r , message=FALSE}
sentiment %>% 
  mutate(n = seq(1, length(value), 1),
         avg = mean(value),
         med = median(value)) %>% 
  ggplot() + 
  geom_smooth(aes(n, value, color = "sentiment value"), se = FALSE) + 
  geom_smooth(aes(n, value, color = "sentiment value regression"), se = FALSE, method = lm) + 
  geom_hline(aes(yintercept = avg, color = "average sentiment value"), linetype = "dashed") + 
  geom_hline(aes(yintercept = med, color = "median sentiment value"), linetype = "dotted") + 
  labs(x = "Order of Speech", 
       y = "Sentiment Value", 
       title = "Sentiment Value Visualization")
```

The sentiment value of the statement means neutral at 0. Positive values represent positive sentiments, while negative values represent negative sentiments. Overall, the mean value of -0.3404 and the median value of -1 both indicate that the overall sentiment of the statements is negative. As with speech length, the mean sentiment value is also significantly higher than the median length. In contrast to speech length, sentiment value decreases over time, meaning that the most recent speech is slightly more negative than the past.

# 3.0 Analysis by Identity #

```{r assignIdentities}
identity <- df %>% 
  mutate(identity = case_when(
    str_detect(speaker, "Rep") ~ "Representative",
    str_detect(speaker, "Sen") ~ "Senator",
    str_detect(speaker, "Congress") ~ "Congressperson",
    str_detect(speaker, "Dr|Prof") ~ "Scholar",
    str_detect(speaker, "President|Obama|Joe Biden|Trump|Clinton|Kamala Harris|Senator Harris|VP") ~ "President",
    str_detect(speaker, "Gates|Zuckerberg|Cook") ~ "Entrepreneur",
    TRUE ~ "NA",
    )) %>% 
  filter(identity != "NA")
```

## 3.1 Word Analysis by Identity ##
```{r wordOccurenceAnalysisByIdentity, message=FALSE}
# processes data into individual words without stop words
word <- identity %>% 
  unnest_tokens(word, speech) %>% 
  anti_join(stop_words, by = "word") %>% 
  filter(!str_detect(word, "it’s|we’re|i’m|that’s|we’ve|you’re|i’ve|there’s|they’re|you’ve"))
# visualization
p = list()
i = 1
identities <- c("Representative", "Senator", "Congressperson", "Scholar", "President", "Entrepreneur")
for (t in identities) {
  p[[i]] <- word %>% 
    filter(identity == t) %>% 
    count(word, sort = TRUE) %>%
    head(35) %>% 
    mutate(word = reorder(word, n)) %>% 
    ggplot(aes(word, n)) + 
    geom_col(position = "dodge") + 
    ggtitle(t) + 
    labs(y = "Number of Occurrences") + 
    guides(x = guide_axis(angle = 60))
  i = i + 1
}
#invisible(sapply(p, print))
grid.arrange(p[[1]], p[[2]], ncol = 2, top=textGrob("The 35 Most Frequent Words for Different Identities"))
grid.arrange(p[[3]], p[[4]], ncol = 2)
grid.arrange(p[[5]], p[[6]], ncol = 2)
```

"People" is the first or second most frequently mentioned word for all the six identities. The most frequently mentioned words for president are those related to the presidential election, such as "fight", "election", "president", "votes", etc. It is interesting to note that scholars and entrepreneurs are not quite fouced on the election, as words related to the election are not in their top 15 most mentioned words. Instead, scholars focus more on public health such as "public", "health", "vaccine", "covid", and "testing". 

```{r wordLengthDistributionByIdentity}
temp <- word %>% 
  group_by(identity) %>% 
  summarize(n = str_count(word, "."), .groups = "drop") # word length

temp %>% 
  filter(n < 15) %>% # remove outliers
  ggplot(aes(y = n)) + 
  geom_boxplot(notch = TRUE) + 
  ggtitle("Word Length Distribution") +
  ylab("Word Length") + 
  facet_grid(.~identity)
```

From the box plot we can see that all the identities except the president have very similar median word lengths. The median word length for the president is significantly smaller. It is worth noting that the 25th word length for all identities is at the same level - 5, which is still higher than the average length of English words of 4.79 [@norvig_2013].

## 3.2 Sentence Analysis by Identity ##
```{r speechLengthDistributionByIdentity}
# count length of sentences
len <- sapply(str_split(identity$speech, " "), length)

sentence <- tibble(n = seq(1,length(len),1),
                   len,
                   avg = mean(len),
                   med = median(len),
                   speech = identity$speech,
                   identity = identity$identity)

sentence %>% 
  filter(len < 200) %>% # remove outliers
  ggplot(aes(y = len)) + 
  geom_boxplot(notch = FALSE) + 
  ggtitle("Speech Length Distribution") + 
  ylab("Speech Length") + 
  facet_grid(.~identity)
```

The box plot shows that scholars have the highest median speech length, with the 75th and 25th speech lengths being among the longest. Conversely, entrepreneurs have the lowest median and 25th speech lengths, and the 75th is the second lowest.

```{r sentenceTypeSummary}
temp <- sentence %>% 
  group_by(identity) %>% 
  summarize(declarative = sum(str_count(speech, "\\.")),
            question = sum(str_count(speech, "\\?")),
            exclamatory = sum(str_count(speech, "!")),
            negative = sum(str_count(speech, "not|Not|’t")),
            affirmative = declarative - negative,
            concession = sum(str_count(speech, c("Though|Although|though|although"))))
# overview
temp
```

```{r sentenceTypeComparisonToneByIdentity}
p <- list()
i = 1
for (t in identities) {
  # sentence type ratio by tone
  p[[i]] <- temp %>% 
  filter(identity == t) %>% 
  pivot_longer(cols = c("declarative", "question", "exclamatory"), 
               names_to = "type", 
               values_to = "value") %>% 
  select(type, value) %>% 
  mutate(ratio = value / sum(value)) %>% 
  ggplot(aes(x = "", y = value, fill = type)) + 
  geom_bar(width = 1, stat = "identity") + 
  geom_text(aes(label = paste(as.character(round(ratio, 4)*100), "%", sep = "")), 
            color = "white", check_overlap = TRUE, vjust = -3) + 
  coord_polar("y") + 
  labs(x = NULL, y = NULL, 
       title = t, 
       fill = "tone") + 
  theme(legend.position = "bottom") + 
  guides(fill = guide_legend(ncol = 1, byrow = TRUE))
  i = i + 1
}
grid.arrange(p[[1]], p[[2]], p[[3]], ncol = 3, top=textGrob("Sentence Type Ratio Based on Tone for Different Identities"))
grid.arrange(p[[4]], p[[5]], p[[6]], ncol = 3)
```

In terms of sentence types based on tone, Representatives, Senators, and Congresspeople asked relatively more questions, while scholars, presidents, and entrepreneurs asked much less answers and mainly answered questions. All of them rarely used exclamations, and academics, presidents, and entrepreneurs never used them.

```{r sentenceTypeComparisonAttitudeByIdentity}
p <- list()
i = 1
for (t in identities) {
  p[[i]] <- temp %>% 
  filter(identity == t) %>% 
  pivot_longer(cols = c("affirmative", "negative"), 
               names_to = "type",
               values_to = "value") %>% 
  select(type, value) %>% 
  mutate(ratio = value / sum(value)) %>% 
  ggplot(aes(x = "", y = value, fill = type)) + 
  geom_bar(width = 1, stat = "identity") + 
  geom_text(aes(label = paste(as.character(round(ratio, 4)*100),"%", sep = "")), 
            color = "white", check_overlap = TRUE, vjust = -3) + 
  coord_polar("y") + 
  labs(x = NULL, y = NULL, 
       title = t, 
       fill = "attitude") + 
  theme(legend.position="bottom")
  i = i + 1
}
grid.arrange(p[[1]], p[[2]], p[[3]], ncol = 3, top=textGrob("Sentence Type Ratio Based on Attitude for Different Identities"))
grid.arrange(p[[4]], p[[5]], p[[6]], ncol = 3)
```

The percentage of negative sentences is at a similar level for all. The percentage of negative sentences of entrepreneurs is slightly higher than that of other identities, and entrepreneur is the only identity that exceeds a quarter. Notably, scholar has the lowest percentage of negative sentences, which is 20.31%. 

```{r concessionComparison}
temp %>% 
  mutate(ratio = concession/declarative) %>% 
  ggplot(aes(identity, ratio, fill = identity)) + 
  geom_bar(stat = "identity") + 
  labs(x = "Identity",
       y = "Proportion",
       title = "Proportion of Concessions in Declarative Sentences",
       subtitle = "by identity")
```

Concession acknowledges that there are many different views to a story. It also shows that all points, positive as well as negative, have been considered before an argument is put forward. Presenting the other side and then arguing against it with valid points can make it very strong. The concession technique is also known used as a method of persuasion and reasoning [@concession_2013]. By comparing the length of conceded sentences used on congressional testimony and hearings by different identities, we can infer which identities are more adept at or require persuasion or reasoning in such contexts. The highest percentage of concessions is given to Congresspeople, while the lowest is given to entrepreneurs and scholars This shows that entrepreneurs and academics do not have many functions of persuasion or reasoning in congressional testimony and hearings. Conversely, Reprentatives, Presidents, and Congresspeople performed more persuasion or reasoning in this context.

## 3.3 Sentiment Analysis by Identity ##
```{r addSentiment}
sentiment <- word %>% 
  inner_join(get_sentiments("bing"), by = "word") %>% 
  inner_join(get_sentiments("afinn"), by = "word")
```

```{r sentimentRatioByIdentity}
p <- list()
i = 1
for (t in identities) {
  p[[i]] <- sentiment %>% 
  filter(identity == t) %>% 
  count(sentiment, sentiment) %>% 
  mutate(ratio = n / sum(n)) %>% 
  ggplot(aes(x = "", y = n, fill = sentiment)) + 
  geom_bar(width = 1, stat = "identity") + 
  geom_text(aes(label = paste(as.character(round(ratio, 4)*100),"%", sep = "")), 
            color = "white", check_overlap = TRUE, vjust = -3, hjust = 0.9) + 
  coord_polar("y") + 
  labs(x = NULL, y = NULL, title =t) + 
  theme(legend.position = "bottom")
  i = i + 1
}
grid.arrange(p[[1]], p[[2]], p[[3]], ncol = 3, top=textGrob("Sentiment Ratio for Different Identities"))
grid.arrange(p[[4]], p[[5]], p[[6]], ncol = 3)
```

The sentiment ratios for Representatives, Senators, Congresspeople, and the Presidents are very close, all with more negative than positive ratios. The sentiment ratios of scholars and entrepreneurs are also very similar but their positive ratios are higher than the negative ratios.

```{r sentimentValueDistributionByIdentity}
# sentiment value
ggplot(sentiment, aes(y = value)) + 
  geom_boxplot(notch = FALSE) + 
  facet_wrap(.~identity) + 
  ggtitle("Sentiment Value Distribution by Identity")
```

The sentiment value distributions of Congresspeople and Representatives are similar, with the medians overlapping with the 25th sentiment value. The medians for entrepreneurs and scholars are both close to the 75th sentiment value, and the sentiment value of entrepreneurs and scholars is similarly distributed. The median for both the president and senators is close to the 25th sentiment value but the president's 25th sentiment value is below -2.5 while the senator's is above -2.5. 

```{r sentimentVisualizationMean, message=FALSE}
sentiment %>% 
  group_by(identity) %>% 
  mutate(avg = mean(value)) %>% 
  distinct(identity, avg) %>% 
  ggplot() + 
  geom_bar(aes(x = identity, y = avg, fill = identity), stat = "identity") + 
  labs(x = "Order of Speech", 
       y = "Average Sentiment Value", 
       title = "Sentiment Value Visualization",
       subtitle = "in the form of mean")
```

The average sentiment of academics is slightly positive by sentiment value mean. Entrepreneurs are slightly more positive than academics. However, all other identities are very negative, especially the president, which is the most negative identity.

```{r sentimentVisualizationMedian}
sentiment %>% 
  group_by(identity) %>% 
  mutate(med = median(value)) %>% 
  distinct(identity, med) %>% 
  ggplot() + 
  geom_bar(aes(x = identity, y = med, fill = identity), stat = "identity") + 
  labs(x = "Order of Speech", 
       y = "Median Sentiment Value", 
       title = "Sentiment Value Visualization",
       subtitle = "in the form of median")
```

The median Sentiment value reflects a similar message to the mean - only entrepreneurs and scholars are positive, while all other identities are negative. By median, congresspeople, presidents, and representatives are tied for the most negative. Entrepreneurs and academics are tied for the most positive.

# 4.0 Conclusion #
In general, congressional testimony and hearings are mainly about American and international political topics and current affairs. In politics, nothing has been more popular in the past few months than the presidential election. In terms of current affairs, the most discussed topic is the epidemic. Therefore, the most frequent words in recent congressional testimony and hearings are related to these topics. The average length of words appearing in this context is 6.959, which is much higher than the average length of English words, which is 4.79 [@norvig_2013]. With the exception of the president, who uses relatively short words, although still above the average length of English words, the median length of words used by people of other identities is very similar, at about 7.

The mean value of 52.28 for speech length is higher than the median of 33, which implies a right-skewed distribution of speech length. Scholars have the longest median speech length and entrepreneurs have the shortest median speech length. Other identities have similar median speech lengths. It is worth noting that recent congressional testimony and hearings have significantly higher speech lengths than previous ones, or that speech lengths have increased over time. Sentences can be classified by tone into declarative, question, and exclamatory sentences. Declarative sentences predominate with 88.67%, followed by questions with 11.32%, and finally exclamations with 0.01. This means that exclamations are rarely used in this context and are therefore not recommended for use in this context. Representatives, senators, and congresspeople have a higher than average percentage of questions, while scholars, presidents, and entrepreneurs rarely ask questions, so they have a lower than average percentage of questions. Sentences can be divided by attitude into affirmative and negative sentences. The overall ratio of affirmative to negative sentences is approximately 4:1, and the ratio is close to this for most identities, with the exception of entrepreneurs, whose ratio is about 3:1. The frequency of the use of concessive sentences may reflect an identity's need for persuasion or reasoning in congressional testimony and hearings. The statistics show that conceded sentences are used most frequently by Congresspeople and least frequently by entrepreneurs and scholars

The overall sentiment in congressional testimony and hearings is negative. The median and mean of sentiment value are both negative. By identity, the speeches of Representatives, Senators, Congresspeople, and Presidents are more **negative** than positive, while the speeches of scholars and entrepreneurs are more **positive** than negative. Sentiment value is also correlated with time. According to the regression analysis, sentiment value decreases over time. In congressional testimony and hearings, statements other than those of scholars and entrepreneurs are predominantly negative, as reflected by their mean and median sentiment values.

In my opinion, the large difference in sentiment is due to the fact that academics and entrepreneurs aim to solve problems, while congresspeople, presidents, representatives, and senators aim to raise issues in that setting. The person who raises the issue should point out its seriousness, thus resulting in a low sentiment value. The problem solver should offer a positive solution, thus making the sentiment value higher.

# Reference #
